|

### 2024-07-02 Drafts/Paper_1/01-analysis_no_age_correction.Rmd
Updated Intro with HB edits

# more density dependence numbers
pa.lam.nf.at.one <- 100*round(no.stock.gam.nf.dat$prop.abund[min(which(no.stock.gam.nf.dat$fit <0))],digits=2)
pa.lam.fish.at.one <- 100*round(no.stock.gam.fish.dat$prop.abund[min(which(no.stock.gam.fish.dat$fit <0))],digits=2)
# What is the minimum abundance at which we get a 2 with the fishing lambdas.
pa.big.threshold <- 0.65
pa.low.threshold <- 0.8
lam.low.threshold <- 0.8
pa.lam.fish.low.bigs <- max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold])
pa.lam.nf.low.bigs <- round(rev(sort(dd.dat$lam.no.fish[dd.dat$prop.abund >= pa.big.threshold]))[2],digits =2)
# What proportion of the stocks had large declines overall, and then the proportion when the population was below 30%
dd.dat.high <- dd.dat |> collapse::fsubset(prop.abund >= 0.3)
prop.low.high.abund <- round(length(which(dd.dat.high$lam.fish < lam.low.threshold)) / nrow(dd.dat.high),digits=3)
prop.low.all <- round(length(which(dd.dat$lam.fish < lam.low.threshold)) / nrow(dd.dat),digits=3)
dd.dat.low <- dd.dat |> collapse::fsubset(prop.abund < 0.3)
prop.low.low.abund <- round(length(which(dd.dat.low$lam.fish < lam.low.threshold)) / nrow(dd.dat.low),digits=3)

>>>>

# more density dependence numbers
pa.lam.nf.at.one <- 100*round(no.stock.gam.nf.dat$prop.abund[min(which(no.stock.gam.nf.dat$fit <0))],digits=2)
pa.lam.fish.at.one <- 100*round(no.stock.gam.fish.dat$prop.abund[min(which(no.stock.gam.fish.dat$fit <0))],digits=2)
# What is the minimum abundance at which we get a 2 with the fishing lambdas.
pa.big.threshold <- 0.65
pa.low.threshold <- 0.8
lam.low.threshold <- 0.8
pa.lam.fish.low.bigs <- round(max(dd.dat$lam.fish[dd.dat$prop.abund >= pa.big.threshold]),digits=2)
pa.lam.nf.low.bigs <- round(rev(sort(dd.dat$lam.no.fish[dd.dat$prop.abund >= pa.big.threshold]))[2],digits =2)
# What proportion of the stocks had large declines overall, and then the proportion when the population was below 30%
dd.dat.high <- dd.dat |> collapse::fsubset(prop.abund >= 0.3)
prop.low.high.abund <- round(length(which(dd.dat.high$lam.fish < lam.low.threshold)) / nrow(dd.dat.high),digits=3)
prop.low.all <- round(length(which(dd.dat$lam.fish < lam.low.threshold)) / nrow(dd.dat),digits=3)
dd.dat.low <- dd.dat |> collapse::fsubset(prop.abund < 0.3)
prop.low.low.abund <- round(length(which(dd.dat.low$lam.fish < lam.low.threshold)) / nrow(dd.dat.low),digits=3)

### 2024-07-02 Drafts/Paper_1/02-intro.Rmd
Updated Intro with HB edits

Intro – life history paragraph, environmental variation paragraph, management ties paragraph, goals.

theoretical expectations related to productivity and life history for various species (e.g. herring vs. Cod) (ties to regional variation in lifetime reproductive rates and doubling time).

Evidence for specific species to make use of environmental conditions – boom in recruitment.

How our understanding of productivity is used in a management context – projections, reference points, risk, (ties directly to density dependence figure).  
Species-environment relationship – is it different from what we expect and how does that influence our capacity for management of exploited fishes.

The underappreciated influence of regional variation in determining recovery potential of exploited teleosts.  - can’t look at a single species and expect it will behave the same way.

Objectives
  - Quantify the life history variability of exploited marine teleosts
  - Explore regional and taxonomic correlates of life history variability
  - Based on the observed life history, quantify the recovery potential of marine teleosts in the absence of fishing

>>>>

Marine fishes were once believed to be essentially inexhaustible and thus extremely resilient to the effects of fishing [@mcintoshFisheriesInterNationalCouncil1919a]. However, high profile collapses of large fisheries and a subsequent lack of rebuilding (cite, cite) have fundamentally challenged this perception. The assumption of resilience originated from early theoretical population dynamics modeling [e.g., @verhulstNoticeLoiQue1838] that culminated in the development of modern fisheries science, largely built around the concept of maximum sustainable yield [MSY, @rickerStockRecruitment1954; @schaeferAspectsDynamicsPopulations1954; @bevertonDynamicsExploitedFish1957]. From its inception, MSY was controversial [@finleyAllFishSea2019; @larkinEpitaphConceptMaximum197], yet the theoretical underpinning in equilibrium concepts and the associated idea that annual reproductive output and/or juvenile survival rates increase as abundance declines (implying harvesting activity will increase the per capita productivity of a population) persisted. The vast majority of modern assessments incorporate a stock-recruit function (cite, cite) making compensatory dynamics a foundational assumption about the life history of a species. Such fisheries assessments implicitly assume that lifetime reproductive rates in the absence of fishing would be expected to be greater than one (Myers cite, cite) and that even heavily-exploited fish populations retain a latent capacity for increase (cite, cite). Although MSY and equilibrium concepts are relatively simple and intuitive, and provide a means of developing tractable mechanistic models, questions remain regarding the applicability of these concepts and whether they adequately reflect the reality of the system being modeled [[@wormRebuildingGlobalFisheries2009; cite cite], particularly for species with markedly different life history characteristics (cite, cite).

Life history characteristics are now considered indicative of a species’ compensatory capacity (cite, cite) and are increasingly used within data-limited assessment approaches to provide management advice (cite). Theory suggests that small fishes, characterized by numerous offspring, rapid growth, early maturity and short lifespans, should have greater compensatory capacity, greater resilience to environmental variability and consequently, be better able to withstand fishing pressure [@kindsvaterTenPrinciplesEvolutionary2016; cite, cite]. Conversely, life histories characterized by longer lifespans and later maturity, or those with lower per-capita reproductive output are considered less resilient (cite). Furthermore, closely related species are anticipated to be more similar than distantly related species owing to a shared evolutionary history (Thorson fishlife), implying less heterogeneity among populations of a single species than among closely-related species. There is a general impression that forage fishes or populations at lower trophic levels are better able to take advantage of favorable environmental conditions and grow more quickly, particularly from low abundance (cite, cite). This resilience should manifest as a high latent capacity for population growth in the absence of fishing, as well as substantial variability in realized population growth rates among years. Dramatic increases in eulecan (FIND OTHER EXAMPLES) following years of particularly low abundance have provided empirical evidence of high compensatory capacity in forage fishes (cites). However, it remains unclear if correlated and compounding ecological and environmental processes (e.g. climate change effects, predatory prey dynamics) can largely obscure the importance of life history on realized productivity, making evolutionary history and life history characteristics a weak foundation for data-poor assessment in light of our changing oceans.

Stock assessment data from harvested marine telosts provide a unique opportunity to explore demographic variability and realized compensatory responses from a conservation biology or population ecology perspective. The long assessment history of these populations means both that their life history characteristics are well-known and that it is possible to quantify realized variability in survival and reproductive output, while accounting for the influence of fisheries. We based our analyses on a database containing age specific abundance information for 77 populations in the north Atlantic and the northeast Pacific Oceans [@charbonneauAgestructuredmarinefishdatabase2022]. By constructing life tables from abundance at age and catch at age data, we calculated common demographic metrics, including  annual population growth rates (cite), doubling time (cite), lifetime reproductive success (cite), and generation time (cite). Comparing the strength and magnitude of variability in realized productivity among species with different life histories as well as among populations of the same species yielded unexpected insights. Our results have implications for sustainable management of these exploited marine teleosts and could be used inform future management actions for populations that have collapsed. More broadly, our results challenged longstanding ideas on the applicability of equilibrium theory, life history theory, and compensatory dynamics to explain expected productivity in fishes.

### 2024-07-02 Drafts/Paper_1/03-methods.Rmd
Updated Intro with HB edits

$$
s_{y,a} =  s_{y,(a-1)} \times l_{y,(a-1)}
$$
### Euler-Lotka

@@

Where $a$ is the age, $\alpha$ is the age at first reproduction, $\omega$ is the maximum age, $\lambda$ is the discrete rate of population growth ($\lambda = e^r$), $s_a$ is the survivorship to age $a$, and $f_a$ is the fecundity of individuals of age $a$. This equation is solved for each year ($y$) in which the data are available. Note that the discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945, @caswellMatrixPopulationModels2001]. Survivorship-at-age and fecundity-at-age were calcualted using the available stock assessment data, which enabled $\lambda$ to be estimated; note that this assumed that each stock represented a discrete population with individual dynamics.

@@

The Euler-Lotka model was fit using an iterative minimization process, where predicted abundance in the following year was compared to the abundance estimate from the stock assessment for the corresponding year ($N_{y+1}$). Where necessary, the annual age-specific fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates from the stock assessment (median difference was `r med.per.diff`). This tolerance ensured that our analyses reflected the same understanding of stock productivity, natural mortality and fecundity as in the current assessments; effectively this methodology treats the abundance estimates from the stock assessments as the 'truth'. The minimization procedure resulted in the final estimates of $\lambda$ being approximately `r med.lam.per.diff` smaller than the initial estimates.

@@

*Here we are treating the plus group as effectively 'terminal', i.e., it assumes that after the last age class the individuals make no contribution, which means these values are probably a bit low, but at this age they really aren't making much of a contribution on average*.

>>>>

$$
s_{y,a} =  s_{y,(a-1)} \times l_{y,(a-1)}
$$

### Euler-Lotka

@@

Where $a$ is the age, $\alpha$ is the age at first reproduction, $\omega$ is the maximum age, $\lambda$ is the discrete rate of population growth ($\lambda = e^r$), $s_a$ is the survivorship to age $a$, and $f_a$ is the fecundity of individuals of age $a$. This equation is solved for each year ($y$) in which the data are available. Note that the discrete time Euler-Lotka equation can be shown to be the characteristic polynomial of the Leslie Matrix, where $f_0$ is the fecundity of the first age class with mature individuals [@leslieUseMatricesCertain1945, @caswellMatrixPopulationModels2001]. Survivorship-at-age and fecundity-at-age were calculated using the available stock assessment data, which enabled $\lambda$ to be estimated; note that this assumed that each stock represented a discrete population with individual dynamics.

@@

The Euler-Lotka model was fit using an iterative minimization process, where predicted abundance in the following year was compared to the abundance estimate from the stock assessment for the corresponding year ($N_{y+1}$). Where necessary, the annual age-specific fecundity and natural mortality estimates were adjusted until the $\lambda$ estimate from the Euler-Lotka equation resulted in an abundance time-series estimate ($N_{y+1}$) that was within 5% of the abundance estimates from the stock assessment (the median difference was `r med.per.diff`). This tolerance ensured that our analyses reflected the same understanding of stock productivity, natural mortality and fecundity as in the current assessments; effectively this methodology treats the abundance estimates from the stock assessments as the 'truth'. The minimization procedure resulted in the final estimates of $\lambda$ being approximately `r med.lam.per.diff`% smaller than the initial estimates.

@@

**NOTE to Y'all: Here we are treating the plus group as effectively 'terminal', i.e., it assumes that after the last age class the individuals make no contribution, which means these values are probably a bit low, but at this age they really aren't making much of a contribution on average**.

### 2024-07-02 Drafts/Paper_1/04-results.Rmd
Updated Intro with HB edits

<!-- Throughout the results we will focus primarily the six most commonly found species in the analysis (*Gadus morhua, Melogrammus aeglefinus, Clupie harengus, Plueronecties platessa, Polluck virens* and *Solea Solea*).  The complete results for all of the populations included in the analysis can be found in the Supplemental material. -->

@@

The overall median population growth rate when excluding the effects of fishing ($\lambda_{FM=0}$) was `r med.lambda.F0`, indicating that there was a latent potential for population growth for these populations of approximately `r med.r.F0`%. When the effect of fishing was accounted for, the median population growth rate ($\lambda_{FM>0}$) declined to `r med.lambda.F`, which suggested that the populations in this analysis may have been over-fished by approximately `r -med.r.F`% annually. Indeed, $\lambda_{FM>0}$ was below one `r prop.lam.fish.lt.1`% of the time. However, for many of the populations included in this analysis large recruitment events resulted in large estimates of $\lambda_{FM>0}$, in some years, this led to a skewed distribution of the $\lambda$ estimates, with these large events being an integral component of the populations population dynamics (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-bx-other-fig)). The mean $\lambda_{FM>0}$ for the populations in this analysis was `r mn.lambda.F` which would suggest there remains scope for population growth even after fishing for most populations, although the mean $\lambda_{FM>0}$ was less than one for `r num.mn.lambda.fish.lt.1` of the `r n.stocks` populations. Finally, the mean $\lambda_{FM>0}$ was lower than the median for just `r n.stocks-n.mn.higher.med.fish` of the `r n.stocks` in this analysis. The majority of these populations (`r n.nw.ice`) were in the central or NW Atlantic, and this included `r n.cod.low.mn`  of the `r n.cod` Atlantic cod (*G. morhua*) populations in this analysis.

There were regional and species specific trends in both $\lambda_{FM=0}$ and $\lambda_{FM>0}$. Haddock (*M. aeglefinus*) and Atlantic cod populations had some of highest variability in lambda, both at the population level and between populations (Figure \@ref(fig:lambda-sd-fig)). For these two species, the variability of $\lambda$ within a population declined as you moved from the Eastern Atlantic to the Western Atlantic (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))). The pattern was more pronounced for Atlantic cod, with populations in the eastern Atlantic tending to have relatively low within population variability. The two other species with populations found in the NW and NE Atlantic (*C.harengus* and *P. virens*) the variability of $\lambda$ between the populations was much lower than for Haddock and Atlantic cod and there were no clear differences between regions for these two species (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig))). This was largely due to the within population $\lambda$ variability being lower than the within population variability of Haddock and Atlantic cod populations in the NE Atlantic (Figure \@ref(fig:lambda-bx-6-fig)). Two other populations (*A. tobianus* and *T. esmarkii*) in the North Sea had highly variably $\lambda's$, though notably they were less variable than the Haddock and Atlantic cod $\lambda's$ in this area (Figure \@ref(fig:lambda-bx-other-fig)). For the remainder of other populations in this analysis, years in which the value of $\lambda_{FM=0}$ exceeded 1.5 were more rare. Exceptions to this included *M. merlangus* in the Celtic Sea, *P. dentatus* and *S. Chrysops* in the NW Atlantic, and the Gulf of Alaska *G. chalcogrammus* population in the Pacific Ocean (Figure \@ref(fig:lambda-bx-other-fig)).

@@

Generally, there was an increase in the variability of the $\lambda$ estimates as abundance declines, largely driven by an increase in the magnitude of the maximum value of $\lambda$ and a small increase in the frequency of low $\lambda$ values (Figure \@ref(fig:dd-overall-plt)). For example, values of $\lambda_{FM>0}$ > `r pa.lam.fish.low.bigs` were not observed at abundances > `100*pa.big.threshold`% of the maximum (similar trends were observed for $\lambda_{FM=0}$, with only one point being above `r pa.lam.nf.low.bigs` when the abundance was > `r 100*pa.big.threshold`% of the maximum). Similarly, the percentage of $\lambda_{FM>0}$ values below `r lam.low.threshold` was `r 100*prop.low.high.abund`% when the proportion of the abundance was >= 0.3, but this increased to `r 100*prop.low.low.abund`% of the data when the proportion of the abundance was below 0.3.

However, these general patterns were highly variable between populations. All of the populations included in this analysis had $\lambda_{FM=0}$ estimates > 1 at their lowest observed abundances (Table \@ref(tab:tab-lambdas) and Figure \@ref(fig:dd-nf-stock-plt)). Populations in the Northwest Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{FM=0}$ estimates at low abundance, while several populations in the North Sea had among the highest $\lambda_{FM=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).  Of the `r n.bl.40` populations that had declined below 40% of the maximum abundance, only `r `n.low.40.nf` of the populations had a $\lambda_{FM=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r `n.low.40.nf` of the populations had $\lambda_{FM>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).

>>>>

@@

The overall median population growth rate when excluding the effects of fishing ($\lambda_{FM=0}$) was `r med.lambda.F0`, indicating that there was a latent potential for population growth for these populations of approximately `r med.r.F0`%. When the effect of fishing was accounted for, the median population growth rate ($\lambda_{FM>0}$) declined to `r med.lambda.F`, which suggested that the populations in this analysis may have been over-fished by approximately `r -med.r.F`% annually. Indeed, $\lambda_{FM>0}$ was below one `r prop.lam.fish.lt.1`% of the time. However, infrequent large recruitment events resulted in large estimates of $\lambda_{FM>0}$ for many populations in a few years. This led to a skewed distribution of the $\lambda$ estimates, with these large events being an integral component of the population dynamics for these populations (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-bx-other-fig)). The mean $\lambda_{FM>0}$ for the populations in this analysis was `r mn.lambda.F` which would suggest there remains scope for population growth even after fishing for most populations, although the mean $\lambda_{FM>0}$ was less than one for `r num.mn.lambda.fish.lt.1` of the `r n.stocks` populations. Finally, the mean $\lambda_{FM>0}$ was lower than the median for just `r n.stocks-n.mn.higher.med.fish` of the `r n.stocks` in this analysis. The majority of these populations (`r n.nw.ice`) were in the central or NW Atlantic, and this included `r n.cod.low.mn`  of the `r n.cod` Atlantic cod (*G. morhua*) populations in this analysis.

There were regional and species specific trends in both $\lambda_{FM=0}$ and $\lambda_{FM>0}$. Haddock (*M. aeglefinus*) and Atlantic cod populations had some of highest variability in $\lambda$, both at the population level and between populations (Figure \@ref(fig:lambda-sd-fig)). For these two species, the variability of $\lambda$ within a population declined as you moved from the Eastern Atlantic to the Western Atlantic (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig)). The pattern was more pronounced for Atlantic cod, with populations in the eastern Atlantic tending to have relatively low within population variability. The two other species with populations found in the NW and NE Atlantic (*C.harengus* and *P. virens*) the variability of $\lambda$ between the populations was much lower than for Haddock and Atlantic cod and there were no clear differences between regions for these two species (Figures \@ref(fig:lambda-bx-6-fig) and \@ref(fig:lambda-sd-fig)). This was largely due to the within population $\lambda$ variability being lower than the within population variability of Haddock and Atlantic cod populations in the NE Atlantic (Figure \@ref(fig:lambda-bx-6-fig)). Two other populations (*A. tobianus* and *T. esmarkii*) in the North Sea had highly variably $\lambda's$, though notably they were less variable than the Haddock and Atlantic cod $\lambda's$ in this area (Figure \@ref(fig:lambda-bx-other-fig)). For the remainder of other populations in this analysis, years in which the value of $\lambda_{FM=0}$ exceeded 1.5 were more rare. Exceptions to this included *M. merlangus* in the Celtic Sea, *P. dentatus* and *S. Chrysops* in the NW Atlantic, and the Gulf of Alaska *G. chalcogrammus* population in the Pacific Ocean (Figure \@ref(fig:lambda-bx-other-fig)).

@@

Generally, there was an increase in the variability of the $\lambda$ estimates as abundance declines, largely driven by an increase in the magnitude of the maximum value of $\lambda$ and a small increase in the frequency of low $\lambda$ values (Figure \@ref(fig:dd-overall-plt)). For example, values of $\lambda_{FM>0}$ > `r pa.lam.fish.low.bigs` were not observed at abundances > `r 100*pa.big.threshold`% of the maximum (similar trends were observed for $\lambda_{FM=0}$, with only one point being above `r pa.lam.nf.low.bigs` when the abundance was > `r 100*pa.big.threshold`% of the maximum). Similarly, the percentage of $\lambda_{FM>0}$ values below `r lam.low.threshold` was `r 100*prop.low.high.abund`% when the proportion of the abundance was >= 0.3, but this increased to `r 100*prop.low.low.abund`% of the data when the proportion of the abundance was below 0.3.

However, these general patterns were highly variable between populations. All of the populations included in this analysis had $\lambda_{FM=0}$ estimates > 1 at their lowest observed abundances (Table \@ref(tab:tab-lambdas) and Figure \@ref(fig:dd-nf-stock-plt)). Populations in the Northwest Atlantic (particularly Atlantic cod) and Alaska had some of the lowest $\lambda_{FM=0}$ estimates at low abundance, while several populations in the North Sea had among the highest $\lambda_{FM=0}$ estimates at low abundance (Table \@ref(tab:tab-lambdas)).  Of the `r n.bl.40` populations that had declined below 40% of the maximum abundance, only `r n.low.40.nf` of the populations had $\lambda_{FM=0}$ estimates < 1 at 40% of their maximum abundance; when the effects of fishing were included `r n.low.40.nf` of the populations had $\lambda_{FM>0}$ estimates below 1 (Table \@ref(tab:tab-lambdas)).

### 2024-07-02 Drafts/Paper_1/08-figures.Rmd
Updated Intro with HB edits

\newpage
```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainded of the stocks in this analysis, plotted by the location of the stock. The abreviated species name is provided on the x axis."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"))

@@

\newpage
```{r dub-vs-sd, echo=F, fig.cap="The number of stocks which doubled in size by a given year with no fishing mortality  The dashed line represents the 77 stocks in the analysis."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"))
```

>>>>

\newpage
```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainder of the stocks in this analysis, plotted by the location of the stock. The abreviated species name is provided on the x axis."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"))

@@

\newpage
```{r dub-vs-sd, echo=F, fig.cap="The recovery potential (low, moderate, or high) of each stock after 20 years compared to the median $\\lambda_{F=0}$ and the standard deviation of $\\lambda_{F=0}$."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"))
```

### 2024-07-02 Drafts/Paper_1/index.Rmd
Updated Intro with HB edits

---
title: |
   "Life history variability influence on the recovery potential of globally exploited teleosts "
french_title: "Titre ici (*Nom latin de l'espèce*)"
author: |
  David. M. Keith^1^ 
  Freya M. Keyser^1^
  Julie M. Charbonneau^2^
  Heather 'The Boss' Bowlby^1^
author_list: "Keith, D.M., Keyser, F.M., Charbonneau, J.M., Bowlby, H.T.B."
address: |
  ^1^Bedford Institute of Oceanography\
     Fisheries and Oceans Canada, 1 Challenger Dr.\
     Dartmouth, Nova Scotia, B2Y 4A2 , Canada\
  \smallskip
  ^2^Simon Fraser University\
     Department of Biology\
french_address: |

>>>>

---
title: |
   "Variability in the recovery potential of globally exploited teleosts "
french_title: "Titre ici (*Nom latin de l'espèce*)"
author: |
  David. M. Keith^1^ 
  Freya M. Keyser^1^
  Julie M. Charbonneau^2^
  Heather 'The Boss' Bowlby^1^
author_list: "Keith, D.M., Keyser, F.M., Charbonneau, J.M., Bowlby, H.T.B."
address: |
  ^1^Bedford Institute of Oceanography\
     Fisheries and Oceans Canada, 1 Challenger Dr.\
     Dartmouth, Nova Scotia, B2Y 4A2 , Canada\
  \smallskip
  ^2^Simon Fraser University\
     Department of Biology\
french_address: |
